Visual diagnostics for constrained optimisation with application to guided tours

### 2021-01-04 paper/paper.Rmd
update pca plot

```{r toy-pca, fig.cap = "1D projection on the 5-variable dataset \\code{boa5} with two optimisers: \\code{search\\_better} and \\code{search\\_geodesic}. The yellow point corresponds to the theoretical best basis [0, 1, 0, 0, 0] with `V2` being the only non-normal variable in the dataset.  The underlying grey points are randomly generated on the 5D space and reduced to 2D via PCA along with all the search points presented. The enlarged color points that colored as the interpolation are the starting points of each algorithm. They are initially simulated with the same starting points but all the bases in \\code{search\\_geodesic} has been flipped positive to ensure that bases with the same projected images but a sign difference are represented by the same point in the plot."}
```

>>>>

```{r toy-pca, fig.height=3, fig.cap = "1D projection on the 5-variable dataset \\code{boa5} with two optimisers: \\code{search\\_better} and \\code{search\\_geodesic}. The yellow point corresponds to the theoretical best basis [0, 1, 0, 0, 0] with `V2` being the only non-normal variable in the dataset.  The underlying grey points are randomly generated on the 5D space and reduced to 2D via PCA along with all the search points presented. The enlarged color points that colored as the interpolation are the starting points of each algorithm. They are initially simulated with the same starting points but all the bases in \\code{search\\_geodesic} has been flipped positive to ensure that bases with the same projected images but a sign difference are represented by the same point in the plot."}
```
